Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-03 manuscript.tex
Mention v1.2 of Tesseroids.

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in the open-source package \textit{Tesseroids}.
It is freely available
online through the software website\footnote{
\href{http://tesseroids.leouieda.com}{http://tesseroids.leouieda.com}}
under the BSD 3-clause open-source license.
An archived version of the source code
is available as part of this article
and online\footnote{
\href{}{\todo[inline]{Replace with the Zenodo DOI for the Tesseroids
source code.}}}.

>>>>

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \textit{Tesseroids}.
It is freely available online
through a persistent archive\footnote{
\href{}{\todo[inline]{Zenodo DOI}}}
or the software website\footnote{
\href{http://tesseroids.leouieda.com}{http://tesseroids.leouieda.com}}.
The software is distributed under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.
